Evolution of Methodologies in Delivering Reliable Software in the European Scientific Arena

### 2018-06-04 paper-ieee-trans.tex
Add the comment back
Explaination of drop of activity in fig4

\item \textit{Unit and Functional testing}.
Changes involving the addition of new functionalities, are required to be tested. \textit{Regression
testing} in this context is accomplished by enforcing the definition and periodic execution
of the tests, covering past fixed issues, to ensure that they are not reintroduced during the development
activities. \textit{Unit testing} completes the source code testing evaluation by focusing on the code's 
internal design. The SQA criteria of {\sl INDIGO--DataCloud} set a recommended threshold of 70\% coverage 
for unit testing. In Fig.~\ref{fig:fig_unittest}, unit testing coverage is compared for each software 
component between the two major releases, denoting an incremental trend over the course of the project: 
code coverage increased from an average value of 50.32\% to 63.34\%, outlined by the respective dates of
the project's first (INDIGO-1) and second (INDIGO-2) releases. By INDIGO-2, half of the software components
(17 out of 32) were over the threshold of the aforementioned project's SQA code coverage recommendation 
(70\%), while three-quarters (24 out of 32) of the product stack exceeded 50\% coverage.

@@

Fig.~\ref{fig:fig_jenkins_CI_builds} shows the evolution, throughout the
{\sl INDIGO--DataCloud}'s first and second releases, of the required test types builds since the
implementation of the CI infrastructure. Automated functional testing coverage were not
available for all the software stack, thus the associated number of builds are fewer.

>>>>

\item \textit{Unit and Functional testing}.
%% Comment from reviewer       
%% These percentages appear as vague approximations by eye, please add the precise numbers rounded.
Changes involving the addition of new functionalities, are required to be tested. \textit{Regression
testing} in this context is accomplished by enforcing the definition and periodic execution
of the tests, covering past fixed issues, to ensure that they are not reintroduced during the development
activities. \textit{Unit testing} completes the source code testing evaluation by focusing on the code's 
internal design. The SQA criteria of {\sl INDIGO--DataCloud} set a recommended threshold of 70\% coverage 
for unit testing. In Fig.~\ref{fig:fig_unittest}, unit testing coverage is compared for each software 
component between the two major releases, denoting an incremental trend over the course of the project: 
code coverage increased from an average value of 50.32\% to 63.34\%, outlined by the respective dates of
the project's first (INDIGO-1) and second (INDIGO-2) releases. By INDIGO-2, 53\% of the software components
(17 out of 32) were over the threshold of the aforementioned project's SQA code coverage recommendation 
(70\%), while 75\% (24 out of 32) of the product stack exceeded 50\% coverage.

@@

Fig.~\ref{fig:fig_jenkins_CI_builds} shows the evolution, throughout the
{\sl INDIGO--DataCloud}'s first and second releases, of the required test types builds since the
implementation of the CI infrastructure. Automated functional testing coverage were not
available for all the software stack, thus the associated number of builds are fewer. Towards the
end of the project, the software development activity slowed the pace but not completely ceased 
as the CI infrastructure is still maintained after the project's end of life.
